%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Georg Bartels}
%\address{http://ai.uni-bremen.de/team/georg\_bartels}
\address{Wartburgstr. 44-46 \\ 28217 Bremen, Germany}
\address{(+49)~$\cdot$~421~$\cdot$~218~$\cdot$~64013 \\ georg.bartels@cs.uni-bremen.de}
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}


{\bf Universit\"at Bremen} \hfill {\em Apr 2013 - present} \\ 
Student Dr-Ing Computer Science \\
Working title: \textit{Movement-aware Control of Everyday Manipulation Tasks}\\ust
Advisor: Prof.~Michael \textsc{Beetz}

{\bf Technische Universit\"at Berlin} \hfill {\em Oct 2005 - Jan 2011}\\
Dipl-Ing Computer Engineering\\
Thesis: \textit{Active Visual Primitives for Perception and Grasping}\\
Specializations: Robotics, Control, and Electronics\\
Advisor: Prof.~Oliver \textsc{Brock}


{\bf Shanghai Jiao Tong University} \hfill {\em Sep 2007 - Aug 2009}\\
Master of Science Computer Applied Technology\\
Thesis: \textit{Automatic Artifact Removal for EEG-based Brain-Computer Interfaces}\\
Specializations: Machine Learning, Artificial Intelligence, and Digital Signal Processing.\\
Advisor: Prof.~Bao-Liang \textsc{Lu}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
	
\begin{rSubsection}{Institute for Artificial Intelligence, Universit\"at Bremen}{Sep 2012 - present}{Research Assistant}{Bremen, Germany}
  \item Research assistant for EU FP7 projects \textit{RoboHow.Cog} and \textit{SAPHARI}.
  \item Teaching assistant for various courses in Bachelor and Master curriculum.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Personal Robotics Lab, Carnegie Mellon University}{Jul 2013 - Sep 2013}{Visiting Scholar}{Pittsburgh, USA}
  \item Constraint-based motion planning algorithms in OpenRAVE.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Division PMA, KU Leuven}{Okt \& Dec 2012}{Visiting Scholar}{Leuven, Belgium}
  \item Constraint-based robot motion control algorithms.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Intelligent Autonomous Systems Group, TU M\"unchen}{Feb 2012 - Aug 2012}{Research Assistant}{M\"unchen, Germany}
  \item Research assistant for EU FP7 projects \textit{RoboHow.Cog} and \textit{SAPHARI}.
  \item Teaching assistant for 'Algorithms and Data-structures'.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Robotics and Biology Labroratory, TU Berlin}{Jan 2011 - Jan 2012}{Student Assistant}{Berlin, Germany}
  \item C/C++ implementation of ROS-drivers for robotic devices and cameras.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Native Instruments GmbH}{Aug 2010 - Jan 2011}{Intern, Hardware Development}{Berlin, Germany}
  \item Assembly, testing, and prototype documentation of sound cards and audio controllers.
  \item Quality assurance during production ramp-up in Shenzhen, China. 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Electronics and Medical Signal Processing Laboratory, TU Berlin}{Oct 2009 - Sep 2010}{Student Assistant}{Berlin, Germany}
  \item Responsible teaching assistant for micro-controller lab course.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{ATN GmbH}{Jan 2006 - Jul 2007}{Intern, Software Development}{Berlin, Germany}
  \item Software development PLC- and micro-controller for light-soldering automation.
  \item Construction, assembly, and start-of-operation of multi-axis light-soldering machines.
\end{rSubsection}

\end{rSection}


%--------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%--------------------------------------------------------------------

\begin{rSection}{Technical Skills}
  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Basic & Prolog, Java, Python, VHDL, Eagle\\
    Intermediate & Latex, Clojure, OpenOffice, Linux, Matlab, SVN\\
	Advanced & Common LISP, C/C++, GIT, ROS
  \end{tabular}
\end{rSection}

%--------------------------------------------------------------------
%	LANGUAGE SKILLS
%--------------------------------------------------------------------

\begin{rSection}{Language Skills}
  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    German & native\\
	English & fluent and confident in negotiations\\
	Chinese & advanced level (certified with HSK-level 5, 10/2009)\\
	French & basic level		
  \end{tabular}
\end{rSection}

%--------------------------------------------------------------------
%	PUBLICATIONS
%--------------------------------------------------------------------

\begin{rSection}{Publications}
  TODO: add me!
\end{rSection}

%--------------------------------------------------------------------
%	OTHER INFORMATION
%--------------------------------------------------------------------

\begin{rSection}{Other Information}
  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Interests & Basketball, Cooking, Soccer, Badminton, Foreign Languages, Reading, Traveling\\
    Award & School of EE and CS Undergraduate Study Award, TU Berlin (2007)
  \end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
